---
title: "Analysis with bootES"
author: "Viktor Gorte"
output: html_document
---

```{r setup, include=TRUE, error=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Setup of libs & data

library(bootES)
library(readr)
library("ggplot2")

data = read_csv(
  file = "study_data_preprocessed.csv",
  col_names = TRUE,
)
```
# General Dataset Analysis

## Participants:
### Age
```{r}
age = data$BG_Age

summary(data$BG_Age[data$BG_Gender == "F"])
summary(data$BG_Age[data$BG_Gender == "M"])

boxplot(
  BG_Age ~ BG_Gender,
  data,
  ylab= "Age",
  xlab= "Gender"
)

```

 Female participants had a minimum age of 21 and a maximum age of 43, whith a mean of 28.
 Male participants had a minimum age of 21 and a maximum age of 67, with a mean of 33.

### Gender
```{r}
gender = data$BG_Gender
#sum of genders has to be divided by 4 since each participants has 4 entries in the dataset (one for each visualization type)
number_of_males = sum(gender == "M") / 4
number_of_females = sum(gender == "F") / 4

print(paste0("Number of Male Participants: ", number_of_males))
print(paste0("Number of Female Participants: ", number_of_females))

gender_distribution = c(number_of_females, number_of_males)
piepercent<- round(100*gender_distribution/sum(gender_distribution), 1)

pie(
  gender_distribution, 
  labels = piepercent,
  main = "Gender Distribution",
  col = rainbow(length(gender_distribution))
)
legend(
  "topright",
  c("Female", "Male"),
  cex = 0.8,
  fill =  rainbow(length(gender_distribution)),
  title = "Distribution in %"
)
```

### Background Information
```{r, ECHO=FALSE}
familiarity_index = data.frame(
  "Value" = c(1:5),
  "Description" = c("Very Unfamiliar", 
                    "Unfamiliar", 
                    "Neither Familiar nor Unfamiliar", 
                    "Familiar", 
                    "Very Familiar"
                    )
  )

daily_usage_index = data.frame(
  "Value" = c(1:6),
  "Description" = c(" < 15 ", 
                    "15 - 30", 
                    "30 - 60", 
                    "60 - 90", 
                    "90 - 120",
                    "120 +"
                    )
  )

weekly_usage_index = data.frame(
  "Value" = c(1:5),
  "Description" = c("Never", 
                    "Once", 
                    "2 - 4 times", 
                    "4 - 8 times", 
                    "More than 8 times"
                    )
  )

usage_mapreading_index = data.frame(
  "Value" = c(1:5),
  "Description" = c("Never", 
                    "Rarely", 
                    "Sometimes", 
                    "Often", 
                    "Very Often"
                    )
  )

```


#### Common Map Types

Familiartiy with Choropleth Maps:
```{r}
#Divided by 4 because each participant is contained 4 times in the dataset, because there are 4 visualization types
familiarity_choropleth = as.matrix(table(data$BG_Familiartiy_Choropleth) / 4)

familiarity_row_names = as.character(familiarity_index[as.numeric(row.names(familiarity_choropleth)),2])

row.names(familiarity_choropleth) = familiarity_row_names

piepercent<- round(100*familiarity_choropleth[,1]/sum(familiarity_choropleth[,1]), 1)

pie(
  familiarity_choropleth, 
  labels = piepercent,
  col = rainbow(length(familiarity_choropleth))
)
legend(
  "topright",
  row.names(familiarity_choropleth),
  cex = 0.8,
  fill =  rainbow(length(familiarity_choropleth)),
  title = "Distribution in %"
)
```


Familiartiy with Graduated Symbol Maps:
```{r}
#Divided by 4 because each participant is contained 4 times in the dataset, because there are 4 visualization types
familiarity_gsm = as.matrix(table(data$BG_Familiartiy_GSM) / 4)

familiarity_row_names = as.character(familiarity_index[as.numeric(row.names(familiarity_gsm)),2])

row.names(familiarity_gsm) = familiarity_row_names

piepercent<- round(100*familiarity_gsm[,1]/sum(familiarity_gsm[,1]), 1)

pie(
  familiarity_gsm, 
  labels = piepercent,
  col = rainbow(length(familiarity_gsm))
)
legend(
  "bottomleft",
  row.names(familiarity_gsm),
  cex = 0.8,
  fill =  rainbow(length(familiarity_gsm)),
  title = "Distribution in %"
)

```

Compared to Choropleth Maps, participants were less familiar with Graduaded Symbol Maps.

#### Geography Knowledge

Familiarity with the Locations of European Countries on a Map:

```{r}
#Divided by 4 because each participant is contained 4 times in the dataset, because there are 4 visualization types
familiarity_eu_countries = as.matrix(table(data$BG_Knowledge_Geography_EU) / 4)

familiarity_row_names = as.character(familiarity_index[as.numeric(row.names(familiarity_eu_countries)),2])

row.names(familiarity_eu_countries) = familiarity_row_names

piepercent<- round(100*familiarity_eu_countries[,1]/sum(familiarity_eu_countries[,1]), 1)

pie(
  familiarity_eu_countries, 
  labels = piepercent,
  col = rainbow(length(familiarity_eu_countries))
)
legend(
  "bottomleft",
  row.names(familiarity_eu_countries),
  cex = 0.8,
  fill =  rainbow(length(familiarity_eu_countries)),
  title = "Distribution in %"
)
```

#### Mobile Device Usage

Distribution of current Mobile Device OS:
```{r}
os_data = data$BG_OS 
#Divided by 4 because each participant is contained 4 times in the dataset, because there are 4 visualization types
os_distribution = table(os_data) / 4

barplot(
  os_distribution,
  beside = TRUE,
  ylab = "Number of Participants",
  xlab = "Operating System",
  main = "Current Mobile Device Operating System \n",
  density=15,
  )

```

Mobile Device Usage for Mapreading Tasks:

```{r}
md_mapreading_usage = as.matrix(table(data$BG_UsageForMapReadingTasks) / 4)

familiarity_row_names = as.character(usage_mapreading_index[as.numeric(row.names(md_mapreading_usage)),2])

row.names(md_mapreading_usage) = familiarity_row_names

barplot(
  md_mapreading_usage, 
  beside = TRUE,
  names.arg = row.names(md_mapreading_usage),
  ylab = "Number of Participants",
  xlab = "Answer",
  density=15
)
```


Daily Mobile Device Usage:

```{r}

daily_usage_data = as.matrix(table(data$BG_Daily_Usage) / 4)

familiarity_row_names = as.character(daily_usage_index[as.numeric(row.names(daily_usage_data)),2])

row.names(daily_usage_data) = familiarity_row_names

barplot(
  daily_usage_data, 
  beside = TRUE,
  names.arg = row.names(daily_usage_data),
  ylab = "Number of Participants",
  xlab = "Minutes",
  density=15
)
```


Weekly Usage of Applications with Maps:

```{r}
weekly_map_app_usage = as.matrix(table(data$BG_Weekly_Usage_MapsApplications) / 4)

familiarity_row_names = as.character(weekly_usage_index[as.numeric(row.names(weekly_map_app_usage)),2])

row.names(weekly_map_app_usage) = familiarity_row_names

barplot(
  weekly_map_app_usage, 
  beside = TRUE,
  names.arg = row.names(weekly_map_app_usage),
  ylab = "Number of Participants",
  xlab = "Frequency",
  density=15
)
```

```{r}
p = ggplot(
  data, 
  aes(x=Confidence_Mean, y=Task_Type),
  ) + geom_boxplot() + coord_flip()
p + labs(
  y = "Task type",
  x = "Confidence (1.0 lowest - 5.0 highest)",
  title= "Confidence distribution per task type"
  )
```

```{r}
p = ggplot(
  data, 
  aes(x=Time_Needed_Mean, y=BG_Gender),
  ) + geom_boxplot() + coord_flip()
p + labs(
  x = "Time needed (seconds)",
  y = "Gender",
  title= "Average time needed for solving tasks per gender"
  )
```

```{r}
p = ggplot(
  data, 
  aes(x=Time_Needed_Mean, y=Task_Type),
  ) + geom_boxplot() + coord_flip()
p + labs(
  x = "Time needed (seconds)",
  y = "Task type"
  )
```

```{r}
p = ggplot(data, aes(x=Time_Needed_Mean, y=BG_OS)) + geom_boxplot()
p + coord_flip()

p = ggplot(
  data, 
  aes(x=Time_Needed_Mean, y=BG_OS),
  ) + geom_boxplot() + coord_flip()
p + labs(
  x = "Time needed (seconds)",
  y = "Operating system",
  title= "Time needed for solving tasks based privatly owned operating system"
  )
```


# Significance Analysis with bootES

```{r}
get_bootES_result <- function(vis1, vis2, task) {
  ##Data Preparation:
  
  v1_v2 = data[data$Vis_Type %in% c(vis1, vis2),]
  v1_v2_task = v1_v2[v1_v2$Task_Type == task,]
  

  contrast_vector = setNames(c(1, -1), c(vis1, vis2))
  
  ## PRINTING BOOTES RESULTS

  print(paste0("Result for ", vis1, " and ", vis2, " for task type ", task , ":"))
        
  bootES(
    v1_v2_task,
    data.col = "Time_Needed_Mean",
    group.col = "Vis_Type",
    contrast = contrast_vector
  )
}
```

## Time needed
```{r}
task = "Distribution"

get_bootES_result("Choropleth Map", "GSM", task)
get_bootES_result("Choropleth Map", "Choriented Map", task)
get_bootES_result("Choropleth Map", "Choriented Mobile", task)
get_bootES_result("Choriented Map", "GSM", task)
get_bootES_result("Choriented Map", "Choriented Mobile", task)
get_bootES_result("GSM", "Choriented Mobile", task)
```

```{r}
task = "Cluster"

get_bootES_result("Choropleth Map", "GSM", task)
get_bootES_result("Choropleth Map", "Choriented Map", task)
get_bootES_result("Choropleth Map", "Choriented Mobile", task)
get_bootES_result("Choriented Map", "GSM", task)
get_bootES_result("Choriented Map", "Choriented Mobile", task)
get_bootES_result("GSM", "Choriented Mobile", task)
```

```{r}
task = "Trend"

get_bootES_result("Choropleth Map", "GSM", task)
get_bootES_result("Choropleth Map", "Choriented Map", task)
get_bootES_result("Choropleth Map", "Choriented Mobile", task)
get_bootES_result("Choriented Map", "GSM", task)
get_bootES_result("Choriented Map", "Choriented Mobile", task)
get_bootES_result("GSM", "Choriented Mobile", task)
```

```{r}
task = "Frequency"

get_bootES_result("Choropleth Map", "GSM", task)
get_bootES_result("Choropleth Map", "Choriented Map", task)
get_bootES_result("Choropleth Map", "Choriented Mobile", task)
get_bootES_result("Choriented Map", "GSM", task)
get_bootES_result("Choriented Map", "Choriented Mobile", task)
get_bootES_result("GSM", "Choriented Mobile", task)
```


## Effectiveness
TRENDS: 
```{r}
task = data[data$Task_Type == "Trend",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Effectivness",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```

Clusters
```{r}
task = data[data$Task_Type == "Cluster",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Effectivness",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```

Distributions: 
```{r}
task = data[data$Task_Type == "Distribution",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Effectivness",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```

Frequencies: 
```{r}
task = data[data$Task_Type == "Frequency",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Effectivness",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Effectivness",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```



## CONFIDENCE
TRENDS: 
```{r}
task = data[data$Task_Type == "Trend",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Confidence_Mean",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```

Clusters
```{r}
task = data[data$Task_Type == "Cluster",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Confidence_Mean",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```

Distributions: 
```{r}
task = data[data$Task_Type == "Distribution",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Confidence_Mean",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```

Frequencies: 
```{r}
task = data[data$Task_Type == "Frequency",]

contrast_vector = setNames(c(1, -1), c("Choropleth Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "GSM"),]

print("Choropleth Map - GSM")

 bootES(
    a,
    data.col = "Confidence_Mean",
    group.col = "Vis_Type",
    contrast = contrast_vector,
  )
 
 
contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Map"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Map"),]

print("Choropleth Map - Choriented Map")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)


contrast_vector = setNames(c(1, -1), c("Choropleth Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choropleth Map", "Choriented Mobile"),]

print("Choropleth Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "GSM"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "GSM"),]

print("Choriented Map - GSM")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("Choriented Map", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("Choriented Map", "Choriented Mobile"),]

print("Choriented Map - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)

contrast_vector = setNames(c(1, -1), c("GSM", "Choriented Mobile"))
a = task[get("Vis_Type", task) %in% c("GSM", "Choriented Mobile"),]

print("GSM - Choriented Mobile")

bootES(
  a,
  data.col = "Confidence_Mean",
  group.col = "Vis_Type",
  contrast = contrast_vector,
)
```